Software Ticket Quality

### 2017-10-16 proposal/mprop.tex
Added new paper to references; formatting

\textbf{What makes a good bug report}\cite{bettenburg2008makes}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
  point of view, based on the typical information found in such a report (e.g. stack traces, screenshots).
\item \textbf{What was the method?}
  The authors conducted a massive survey with over 450 respondents. The survey was online and it targeted
  developers from Mozilla, Apache and Eclipse.
\item \textbf{What did they learn?}
  The main conclusion of this research paper was that well written bug reports will more likely get the 
  attention of the developers. Thus, including steps to reproduce the bugs or stack traces proved to increase
  the quality of the bug report. Also, an important achievement reached by the authors was the development of
  a prototype tool called Cuezilla that could estimate, with an accuracy rate of 31\-48\%, the quality of a bug
  report.
\item \textbf{Relevance to our work}: it is relevant to our research in that it provides valuable insight into 
  what makes for a good bug report based on actual professionals' opinions.
\end{itemize}

@@

\textbf{Software Development Waste}\cite{sedano2017software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to identify main types of waste in software
    development projects.
  \item \textbf{What was the method?}
    They conducted a participant-observation study over a long period of time
    at Pivotal, a consultancy software development company. They also interviewed
    multiple engineers and balanced theoretical sampling with analysis to achieve
    the conclusions.
  \item \textbf{What did they learn?}
    They found out there are nine main types of waste in software projects:
    \begin{itemize}
      \item building the wrong feature or product;
      \item mismanaging backlog;
      \item extraneous cognitive load;
      \item rework;
      \item ineffective communication;
      \item waiting/multitasking;
      \item solutions too complex;
      \item psychological distress.
  \item \textbf{Relevance to our work}: this paper complements the previous 
    one on waste identification\cite{Korkala2014WasteIdentification}.
\end{itemize}

>>>>

\textbf{What makes a good bug report}\cite{bettenburg2008makes}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The main goal of the paper was to investigate the \textbf{quality of bug reports} from a developer's
  point of view, based on the typical information found in such a report (e.g.\ stack traces, screenshots).
\item \textbf{What was the method?}
  The authors conducted a massive survey with over 450 respondents. The survey was online and it targeted
  developers from Mozilla, Apache and Eclipse.
\item \textbf{What did they learn?}
  The main conclusion of this research paper was that well written bug reports will more likely get the 
  attention of the developers. Thus, including steps to reproduce the bugs or stack traces proved to increase
  the quality of the bug report. Also, an important achievement reached by the authors was the development of
  a prototype tool called Cuezilla that could estimate, with an accuracy rate of 31\-48\%, the quality of a bug
  report.
\item \textbf{Relevance to our work}: it is relevant to our research in that it provides valuable insight into 
  what makes for a good bug report based on actual professionals' opinions.
\end{itemize}

@@

\textbf{Software Development Waste}\cite{sedano2017software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to identify main types of waste in software
    development projects.
  \item \textbf{What was the method?}
    They conducted a participant-observation study over a long period of time
    at Pivotal, a consultancy software development company. They also interviewed
    multiple engineers and balanced theoretical sampling with analysis to achieve
    the conclusions.
  \item \textbf{What did they learn?}
    They found out there are nine main types of waste in software projects:
    \begin{itemize}
      \item building the wrong feature or product;
      \item mismanaging backlog;
      \item extraneous cognitive load;
      \item rework;
      \item ineffective communication;
      \item waiting/multitasking;
      \item solutions too complex;
      \item psychological distress.
      \item \textbf{Relevance to our work}: this paper complements the previous 
    one on waste identification\cite{Korkala2014WasteIdentification}.
    \end{itemize}
\end{itemize}
